Giant Low Surface Brightness Galaxies As Merger Remnants

### 2018-05-16 glsb.tex
updated to aastex

%\documentclass[12pt,preprint]{aastex}
\documentclass{emulateapj}
\usepackage{url}
%\usepackage{natbib}
%\usepackage{xspace}
\def\arcsec{$^{\prime\prime}$}
\bibliographystyle{apj}
\newcommand\degree{{^\circ}}
\newcommand\surfb{$\mathrm{mag}/\square$\arcsec}
\newcommand\Gyr{\rm{~Gyr}}
\newcommand\msun{\rm{M}_\odot}
\newcommand\kms{km s$^{-1}$}
\newcommand\al{$\alpha$}
\newcommand\ha{$\rm{H}\alpha$}
\newcommand\hb{$\rm{H}\beta$}
\newcommand\HI{\ion{H}{1}}

@@

\author{Peter Yoachim\altaffilmark{1}, Denise Schmitz\altaffilmark{4}, Sarah Loebman\altaffilmark{2}, SungWon Kwak\altaffilmark{5,6}, Victor P. Debattista\altaffilmark{3}
  }

\altaffiltext{1}{Department of Astronomy, University of Washington, Box 351580,
Seattle WA, 98195}
\altaffiltext{2}{University of Michigan}
\altaffiltext{3}{Jeremiah Horrocks Institute, University of Central Lancashire, Preston PR1 2HE, UK.}
\altaffiltext{4}{California Institute of Technology}
\altaffiltext{5}{Center for the Exploration of the Origin of the Universe
(CEOU), Department of Physics \& Astronomy, Seoul
National University, Seoul 151-742, Republic of Korea}
\altaffiltext{6}{Korea Astronomy and Space Science Institute, Daejeon 305-348, Republic of Korea}

>>>>

\documentclass[12pt]{aastex62}
%\documentclass[12pt,preprint]{aastex}
%\documentclass{emulateapj}
\usepackage{url}
%\usepackage{natbib}
%\usepackage{xspace}
\def\arcsec{$^{\prime\prime}$}
\bibliographystyle{apj}
\newcommand\degree{{^\circ}}
\newcommand\surfb{$\mathrm{mag}/\square$\arcsec}
\newcommand\Gyr{\rm{~Gyr}}
\newcommand\msun{\rm{M}_\odot}
\newcommand\kms{km s$^{-1}$}
\newcommand\al{$\alpha$}
\newcommand\ha{$\rm{H}\alpha$}
\newcommand\hb{$\rm{H}\beta$}
\newcommand\HI{\ion{H}{1}}

@@

\correspondingauthor{Peter Yoachim}
\email{yoachim@uw.edu}

\author[0000-0003-2874-6464]{Peter Yoachim}
\altaffiliation{Department of Astronomy, \\
University of Washington, Box 351580,\\
Seattle WA, 98195}

\author{Denise Schmitz}
\altaffiliation{California Institute of Technology}

\author{Sarah Loebman}
\altaffiliation{University of Michigan}

\author{SungWon Kwak}
\altaffiliation{Center for the Exploration of the Origin of the Universe (CEOU),\\
 Department of Physics \& Astronomy, Seoul\\
National University, Seoul 151-742, Republic of Korea}
\altaffiliation{Korea Astronomy and Space Science Institute, \\
Daejeon 305-348, Republic of Korea},

\author{Victor P. Debattista}
\altaffiliation{Jeremiah Horrocks Institute, \\
University of Central Lancashire, Preston PR1 2HE, UK.}
